### 2011-06-19 manuscript.tex
Edits from Mom's proofreading.

``Sascha, the top feed is ready,'' called a voice near the window.  The Office of Internal Affairs, despite the lofty title, was a cramped, stuffy office that contained five desks, eighteen computers and other office machines, and could comfortably fit three bodies, provided that the bodies were reasonably proportioned and were not given to clumsiness.  Sascha sat facing the north wall, preferring not to be distracted by the constant movement of his colleagues.  Jill, the office technology specialist, sat near the windows where she could keep a watchful eye on the myriad devices that kept the room warm.  Sean, the interdepartmental liason (the External Internal Affairs Spokesman, Sascha called him), worked at a stand-up desk that was mounted on the west wall between the two oat doors.  The remainder of the 600 square foot space was a labyrinth of machines, cables clamped to the floor with black duct tape, stacks of official university records, and the occasional abandoned coffee mug.  The abundance of machines meant that one window stayed propped open year-around.

@@

Marcel leaned back in his seat and tilted his head to the right, clearly wondering what Jesse had been in Jesse's mind as he spoke those words.  It was a moment before he spoke again.  ``You offer us money, Jesse?''

@@

``It was known that he saw visited women other than his wife.  After he declared his candidacy, this secret became known to the public.  It is not clear how this information became known.  He never recovered from the stain on his reputation, and he lost the election.  It was soon after that his family left the country, and we see now that he reaches through his son in an attempt to blame us for his past mistakes.''

@@

``Give me ten,'' Sascha said, and quietly flipped his phone closed.  His pulse had quickened.  The information that Jill had given him, thought it probably seemed suspicous, would seem ultimately inconsequential to anyone else.  To Sascha, though, the news was unwelcome.  He knew the scheduling system very well, and he knew his building.  Someone had scheduled maintenance for the room where Jesse normally worked, and someone---probably the same someone---had cancelled the service ticket.  By itself, that could be attributed to a mistake by the person scheduling the ticket.  With the door ajar on a secured office that was normally occupied during the day, the situation changed.

@@

When the police chief had learned that Sascha had destroyed the bug by sending down a sink drain, he was furious.  Sascha's instinct had been to isolate and then eliminate the threat, and he had done so.  Unfortunately, this was no time for battlefield tactics.  It the police had access to the bug, then they had a fighting chance of tracking down a receiver and the person responsible for installing the equipment.  As it stood, they could do nothing but encourage Jesse to change his habits and keep a watchful eye for anything suspicious.

@@

Sascha laughed, holding up his hands.  ``I was just joking, dude.  You did the right thing, and any judge or jury worth their salt will see that.  Shelby has his agenda.  He made that abundantly clear in the paper.''

@@

Sascha, for his part, was intrigued by the idea of sitting in on, and even being allowed to participate in, a criminal interrogation.  What would they learn next week?  Maybe the guy would roll over on his bosses.  Maybe he would give the FBI some dirt on few politicians in Europe.  Maybe he would go on endlessly about his skills as a spy for hire.  The odds of convincing him to do anything were poor.  The NYPD could only drop hints and try to lead him in directions that might reveal something interesting.  Hearding cats would be easier by comparison.

@@

``Yeah,'' Jesse said, ``but apparently I don't think behind very well.  We never would have gotten anywhere with this on our own.''  He paused.  ``I wish that there was some way that I could prepare myself for the questioning.  Maybe we should sit down tomorrow and build a list of possible connections.  All the reasons that he might have for watching us, and the people who might pay him to do it.  I have a list of our projects on my laptop, and it would be easy to pull out all the one that touched European countries.''

@@

As they reached the door, Sascha glanced toward the front door.  At that moment, the door of a limousine opened on the street, and the noise level more than doubled.  Flashbulbs exploded across the chamber, leaving Jesse and Sascha dazed.  Sascha pulled the door up and its tracks, grabbed Jesse's arm, and hauled him through the door.  As he emerged on the other side, the door slid closed with a metallic bang.  A group of puzzled onlookers stared at them.  A young Asian man began to fumble with his camera, and Sascha gave Jesse another firm tug to get his feet moving.  They were out of sight before the man could take the photo.

@@

``Just a minute,'' Jesse said as he walked with Sascha toward the elevator.  He ducked into the men's room and pulled the USB stick from his pocket.  One of the only remaining copies in existence.  He snapped the eletronic stick in half, dropped the pieces into the first toilet and kicked the lever on the side.  With a certain satisfaction, he watched them bubble to the bottom of the bowl and then disappear.

>>>>

``Sascha, the top feed is ready,'' called a voice near the window.  The Office of Internal Affairs, despite the lofty title, was a cramped, stuffy office that contained five desks, eighteen computers and other office machines, and could comfortably fit three bodies, provided that the bodies were reasonably proportioned and were not given to clumsiness.  Sascha sat facing the north wall, preferring not to be distracted by the constant movement of his colleagues.  Jill, the office technology specialist, sat near the windows where she could keep a watchful eye on the myriad devices that kept the room warm.  Sean, the interdepartmental liason (the External Internal Affairs Spokesman, Sascha called him), worked at a stand-up desk that was mounted on the west wall between the two oak doors.  The remainder of the 600 square foot space was a labyrinth of machines, cables clamped to the floor with black duct tape, stacks of official university records, and the occasional abandoned coffee mug.  The abundance of machines meant that one window stayed propped open year-around.

@@

Marcel leaned back in his seat and tilted his head to the right, clearly wondering what had been in Jesse's mind as he spoke those words.  It was a moment before he spoke again.  ``You offer us money, Jesse?''

@@

``It was known that he visited women other than his wife.  After he declared his candidacy, this secret became known to the public.  It is not clear how this information became known.  He never recovered from the stain on his reputation, and he lost the election.  It was soon after that his family left the country, and we see now that he reaches through his son in an attempt to blame us for his past mistakes.''

@@

``Give me ten,'' Sascha said, and quietly flipped his phone closed.  His pulse had quickened.  The information that Jill had given him, though it probably seemed suspicous, would seem ultimately inconsequential to anyone else.  To Sascha, though, the news was unwelcome.  He knew the scheduling system very well, and he knew his building.  Someone had scheduled maintenance for the room where Jesse normally worked, and someone---probably the same someone---had cancelled the service ticket.  By itself, that could be attributed to a mistake by the person scheduling the ticket.  With the door ajar on a secured office that was normally occupied during the day, the situation changed.

@@

When the police chief had learned that Sascha had destroyed the bug by sending it down a sink drain, he was furious.  Sascha's instinct had been to isolate and then eliminate the threat, and he had done so.  Unfortunately, this was no time for battlefield tactics.  It the police had access to the bug, then they had a fighting chance of tracking down a receiver and the person responsible for installing the equipment.  As it stood, they could do nothing but encourage Jesse to change his habits and keep a watchful eye for anything suspicious.

@@

Sascha laughed, holding up his hands.  ``I was just joking, dude.  You did the right thing, and any judge or jury worth its salt will see that.  Shelby has his agenda.  He made that abundantly clear in the paper.''

@@

Sascha, for his part, was intrigued by the idea of sitting in on, and even being allowed to participate in, a criminal interrogation.  What would they learn next week?  Maybe the guy would roll over on his bosses.  Maybe he would give the FBI some dirt on few politicians in Europe.  Maybe he would go on endlessly about his skills as a spy for hire.  The odds of convincing him to do anything were poor.  The NYPD could only drop hints and try to lead him in directions that might reveal something interesting.  Herding cats would be easier by comparison.

@@

``Yeah,'' Jesse said, ``but apparently I don't think behind very well.  We never would have gotten anywhere with this on our own.''  He paused.  ``I wish that there was some way that I could prepare myself for the questioning.  Maybe we should sit down tomorrow and build a list of possible connections.  All the reasons that he might have for watching us, and the people who might pay him to do it.  I have a list of our projects on my laptop, and it would be easy to pull out all the ones that touched European countries.''

@@

As they reached the door, Sascha glanced toward the front door.  At that moment, the door of a limousine opened on the street, and the noise level more than doubled.  Flashbulbs exploded across the chamber, leaving Jesse and Sascha dazed.  Sascha pulled the door up on its tracks, grabbed Jesse's arm, and hauled him through the door.  As he emerged on the other side, the door slid closed with a metallic bang.  A group of puzzled onlookers stared at them.  A young Asian man began to fumble with his camera, and Sascha gave Jesse another firm tug to get his feet moving.  They were out of sight before the man could take the photo.

@@

``Just a minute,'' Jesse said as he walked with Sascha toward the elevator.  He ducked into the men's room and pulled the USB stick from his pocket.  One of the only remaining copies in existence.  He snapped the electronic stick in half, dropped the pieces into the first toilet and kicked the lever on the side.  With a certain satisfaction, he watched them bubble to the bottom of the bowl and then disappear.
